\documentclass[11pt,a4paper]{article}
\usepackage[german,english]{babel}
\usepackage{xeCJK} % For Chinese characters
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}

% Page setup
\geometry{margin=2.5cm}

% Chinese font setup
\IfFontExistsTF{Noto Sans CJK SC}{
    \setCJKmainfont{Noto Sans CJK SC}
}{
    \IfFontExistsTF{FandolSong}{
        \setCJKmainfont{FandolSong}
    }{
        \IfFontExistsTF{SimSun}{
            \setCJKmainfont{SimSun}
        }{
            \IfFontExistsTF{STSong}{
                \setCJKmainfont{STSong}
            }{
                \setCJKmainfont{AR PL UMing CN}
            }
        }
    }
}

\title{World Product Gallery\\
世界产品画廊\\
Weltproduktgalerie}
\author{Project Statement}
\date{\today}

\begin{document}

\maketitle

\section*{Project Statement / Projektbeschreibung / 项目说明}

\textbf{English:}

World Product Gallery: A bottom-up Qingming Riverside Scene (清明上河图) of world products and supply chains.

This project aims to create a comprehensive, detailed visualization and analysis of products from around the world, examining their supply chains from a bottom-up perspective. Inspired by the famous Chinese painting "Along the River During the Qingming Festival" (清明上河图), which depicts the intricate details of daily life and commerce in ancient China, this gallery seeks to capture the complexity and interconnectedness of modern global supply chains through detailed product analysis.

Each product entry includes:
\begin{itemize}
    \item Product description and specifications
    \item Market analysis and positioning
    \item Manufacturer information and location
    \item Market entities and stakeholders
    \item Detailed supply chain analysis (raw materials, production, distribution)
    \item Market dynamics and competitive landscape
    \item Geographic visualizations and maps
    \item Comprehensive business insights
\end{itemize}

The analysis is presented in three languages (German, English, and Chinese) to reflect the global nature of modern commerce and supply chains.

\vspace{0.5cm}

\textbf{Deutsch:}

World Product Gallery: Eine von unten nach oben aufgebaute Qingming-Flusslandschaft (清明上河图) der Weltprodukte und Lieferketten.

Dieses Projekt zielt darauf ab, eine umfassende, detaillierte Visualisierung und Analyse von Produkten aus aller Welt zu erstellen, wobei ihre Lieferketten aus einer Bottom-up-Perspektive untersucht werden. Inspiriert vom berühmten chinesischen Gemälde "Qingming-Flusslandschaft" (清明上河图), das die komplexen Details des täglichen Lebens und Handels im alten China darstellt, versucht diese Galerie, die Komplexität und Vernetzung moderner globaler Lieferketten durch detaillierte Produktanalysen zu erfassen.

Jeder Produkteintrag umfasst:
\begin{itemize}
    \item Produktbeschreibung und Spezifikationen
    \item Marktanalyse und Positionierung
    \item Herstellerinformationen und Standort
    \item Marktakteure und Stakeholder
    \item Detaillierte Lieferkettenanalyse (Rohstoffe, Produktion, Vertrieb)
    \item Marktdynamik und Wettbewerbslandschaft
    \item Geografische Visualisierungen und Karten
    \item Umfassende Geschäftseinblicke
\end{itemize}

Die Analyse wird in drei Sprachen (Deutsch, Englisch und Chinesisch) präsentiert, um den globalen Charakter des modernen Handels und der Lieferketten widerzuspiegeln.

\vspace{0.5cm}

\textbf{中文:}

世界产品画廊：从底向上的世界产品及供应链的清明上河图

本项目旨在创建对世界各地产品的全面、详细的可视化和分析，从自下而上的角度审视其供应链。受著名的中国画《清明上河图》的启发，该画描绘了古代中国日常生活和商业的复杂细节，本画廊试图通过详细的产品分析来捕捉现代全球供应链的复杂性和相互关联性。

每个产品条目包括：
\begin{itemize}
    \item 产品描述和规格
    \item 市场分析和定位
    \item 制造商信息和位置
    \item 市场实体和利益相关者
    \item 详细的供应链分析（原材料、生产、分销）
    \item 市场动态和竞争格局
    \item 地理可视化和地图
    \item 全面的商业洞察
\end{itemize}

分析以三种语言（德语、英语和中文）呈现，以反映现代商业和供应链的全球性。

\end{document}
